### 2020-01-30 Mathematical Statistics/05_conf_int_bootstrap.rmd
never enough bootstrap
(NEED MORE BOOTSTRAP)

ggplot(MathAnxiety, aes(Gender, AMAS)) +
   geom_boxplot(aes(color = Gender))

@@

for(i in 1:N)
{
   samp.target <- sample(prices.target, size = length(prices.target), replace = T)
   samp.walmart <- sample(prices.walmart, size = length(prices.walmart), replace = T)

@@

for(i in 1:N)
{
   samp.target <- sample(prices.target, size = length(prices.target), replace = T)
   samp.walmart <- sample(prices.walmart, size = length(prices.walmart), replace = T)

@@

The bootstrap confidence intervals include zero, so there is not sufficent evidence here to support the claim that the prices have a statistically significant difference.

>>>>

ggplot(MathAnxiety, aes(Gender, AMAS)) +
   geom_boxplot(aes(fill = Gender))

@@

for(i in 1:N)
{
   index <- sample(length(prices.target), size = length(prices.target), replace = T)

   samp.target <- prices.target[index]
   samp.walmart <- prices.walmart[index]

@@

for(i in 1:N)
{
   # paired data, must use the same products from each company
   index <- sample(length(prices.target), size = length(prices.target), replace = T)

   samp.target <- prices.target[index]
   samp.walmart <- prices.walmart[index]

@@

The bootstrap confidence intervals suggest that there is a statistically significant difference in prices (Target being more expensive than Walmart). The Quaker Oats cereal made a difference.

### 5.19

Do chocolate and vanilla ice cream have the same number of calories?

The data set Ice Cream contains calorie information for a sample of brands of chocolate and vanilla ice cream.

```{r}
IceCream <- data.table(read.csv(paste0(data.dir, "IceCream.csv"),
                                 header = T))
```

a.) Compute summary statistics of the calories for the two flavors.

icecream <- IceCream %>%
   mutate(Vanilla = VanillaCalories,
          Chocolate = ChocolateCalories) %>%
   select(Vanilla, Chocolate) %>%
   melt(variable.name = "Flavor", value.name = "Calories") %>%
   as.data.table()

stopifnot(nrow(icecream) == nrow(IceCream) * 2)

ggplot(icecream, aes(Calories, group = Flavor)) +
   geom_density(aes(fill = Flavor), alpha = .35)

ggplot(icecream, aes(Flavor, Calories, fill = Flavor)) +
   geom_boxplot()
```

b.) Use the bootstrap to determine whether or not there is a difference in the mean number of calories.

```{r}
calories.vanilla <- icecream[Flavor == "Vanilla"]$Calories
calories.chocolate <- icecream[Flavor == "Chocolate"]$Calories

observed <- mean(calories.chocolate) - mean(calories.vanilla)

for(i in 1:N)
{
   # paired data, must use the same samples from chocolate and vanilla (ie, same manufacture)
   index <- sample(length(calories.vanilla), length(calories.vanilla), replace = T)

   v.samp <- calories.vanilla[index]
   c.samp <- calories.chocolate[index]

   bootstrap.values[i] <- mean(c.samp) - mean(v.samp)
}

ggplot(data.table(values = bootstrap.values), aes(values)) +
   geom_histogram(aes(y = ..density.., fill = ..count..), bins = 30) +
   geom_density(col = "darkorange") +
   geom_vline(xintercept = observed)

bootstrap.bias / bootstrap.se

There appers to be a statistically difference in the amount of calories (Chocolate having more, by approx 4-12 on average).

### 5.20

In a remark at the end of Section 5.4.1, we mentioned that the procedure for bootstrapping the difference of medians is different than for thee mean.

Import the data set Diving2017.
